An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
proofreading of section 3

\section{Segmentation of text into words}
\label{sec:segtext}
In this section we explain the first step in the process of extracting individual characters from a text image: i.e. word extraction.
Word extraction from text images has many possible approaches, but in this paper we focus solely on the word contouring approach, pointed out by following paper \cite{WordSegm} to be a successfull word extraction approach.

With this approach we extract the contours of the words in a given text image. Through postprocessing techniques we can rearrange these extracted words into lines.
The proposed approach focusses solely on text images, and does not take into account non-textual areas found in the input image.
Additional techniques for page segmentation can be utilized depending on the situation.

\subsection{Binarization}
We start with binarizing the text image.

To achieve this there are a lot of thresholding algorithms to choose from, but the one we use is a combination of Gaussian blur in combination with Otsu's thresholding algorithm.

The Gaussian blur will smoothen the noise in the image and smoothen the edges of the text.
%TODO:: Otsu reference
Otsu's tresholding algorithm will deliver adequate result for noisy text documents.
The choise of tresholding algorithm depends mostly on the intended purposes of the algorithm.
Additional noise removal techniques and other preprocessing techniques may be required for a better result when processing very noise-heavy images.

\subsection{Contouring}
Our text segmentation approach is based on finding contours in the text image.
We can find these contours using %TODO:: reference paper contouring suzuki85
Through postprocessing we can recover the original words from these extracted contours.

\subsection{Postprocessing}
We can remove the incorrect contours generated by the contouring algorithm through postprocessing.
Secondly we will reconnect words that were split because they are not written in a single stroke.

\subsubsection{Contour removal}
The contouring algorthm can create incorrect contours because of left-over noise in the image.
The tool we will use to remove these incorrect contours is the bounding box we can draw around a contour.
This bounding box is the smallest rectangle containing said contour, and it will allow us to easily compare contour positions in the text image.

Firstly we remove the contours of which the bounding box is contained by the bounding box of a second contour.
We can do this because the text segmentation process will return the word in the image contained by its bounding box, so we will not change  % TODO:: NOTATION

Secondly we remove contours that are too small to contain parts of a word.
The contouring algorithm will generate contours of noise and punctuation.
These contours we do not want to process, so we will filter them out.

This is done by taking the average height of all the found contours in the text.
Iteratively we remove remove the contours with a height lesser than the a predetermined threshold,
\vspace{-5px}
\begin{equation}
    threshold = averageHeight * removalMultiplier
\end{equation}
with the $removalMultiplier$ initialized on $2 / 3$ as chosen value.

\subsubsection{Contour combination}
With the excess contours removed, we begin to reconstruct the original words from the text.
We do this by combining multiple contours into one where a word was separated into multiple parts.
We have created a straightforward overlapping algorithm, that combines word segments based on the overlap between the bounding box of their contours.

We have a parameter for the allowed gap between parts of the same word, and one for the minimal y-axis overlap of both their boundingboxes.

\begin{equation} %TODO:: FIX INDENTATION
    if \\ 
        wordXaxisGap < \\
            averageWordWidth * (1 / (averageCharacterCount * 2) )\\
        and \\
        wordYaxisOverlap > \\
        min(word1.height, word2.height) * requiredYaxisOverlap\\
    then \\
        combineWords
\end{equation}
The optimal parameters we found are:

\noindent 
$averageCharacterCount = 8$ and

\noindent
$requiredYaxisOverlap = 1/2$

With these conditions fulfilled, we combine both contours into one single contour, containing the found word.

@@

\subsection{Line selection}
With the words extracted from the text, the next goal is to reconstruct the original text.
We will need to order these words into lines 
For the line selection process, an iterative algorithm, Algorithm \ref{alg:linereconstr}, is used.

This algorithm reorders the found words in lines, and return these lines as ordered in the original text image.

>>>>

\section{Segmentation of text into words}
\label{sec:segtext}
In this section we explain the first step in the process of extracting individual characters from a text image: i.e. word extraction.
Word extraction from text images has many possible approaches, but in this paper we focus solely on the word contouring approach, pointed out by following paper \cite{WordSegm} to be a successful word extraction method.
With this method we extract the contours of the words in a given text image. Through postprocessing techniques we can rearrange these extracted words into lines.
The proposed approach focusses solely on text images, and does not take into account non-textual areas found in the input image.
Additional techniques for page segmentation can be utilized depending on the situation.

\subsection{Binarization}
We start with binarizing the text image. To achieve this there are a lot of thresholding algorithms to choose from, but the one we use is a combination of Gaussian blur in combination with Otsu's thresholding algorithm. \cite{Otsu79} 
The Gaussian blur will smoothen the noise in the image and smoothen the edges of the text.
Otsu's tresholding algorithm will deliver adequate result for noisy text documents.
The choise of tresholding algorithm depends mostly on the intended purposes of the algorithm.
Additional noise removal techniques and other preprocessing techniques may be required for a better result when processing images with much noise.

\subsection{Contouring}
Our text segmentation approach is based on finding contours in the text image.
We can find these contours using the algorithm \cite{Suzuki85}.
Through postprocessing we can recover the original words from these extracted contours.

\subsection{Postprocessing}
We remove the incorrect contours generated by the contouring algorithm through postprocessing.
Next we reconnect words that are split because they are not written in a single stroke.

\subsubsection{Contour removal}
The contouring algorithm can create incorrect contours because of left-over noise in the image.
The tool we will use to remove these contours is a bounding box drawn around the contour.
This bounding box is the smallest rectangle containing the contour, it allows us to easily compare positions of contours in the text image.

Firstly we remove the contours of which the bounding box is inside the box of another contour.
This is possible as text segmentation returns the word in the image contained by its biggest bounding box. 
Secondly we remove contours that are too small to contain possible word parts. These contours consist of noise and punctuation.
These contours are neglected by taking the average height of all the found contours in the text.
We remove all of the contours with a height smaller than $average height * (2/3)$.

\subsubsection{Contour combination}
The leftover contours are used to to reconstruct the original words from the text.
This is done by combining multiple contours which consist of parts of words belonging to the same word. 
We have created an algorithm that combines word segments. It is uses the overlap between the bounding box of their contours to find possible combinations.

% Hoe heet die parameter? Wat is de waarde van de parameter. Plaats de namen, de waardes en hun uitleg samen, plaats hier geen algoritme/formule tussen. 
We have a parameter for the allowed gap between parts of the same word, and one for the minimal y-axis overlap of both their boundingboxes.

\begin{equation} %TODO:: FIX INDENTATION, Plaats zoiets in algorithmic
    if \\ 
        wordXaxisGap < \\
            averageWordWidth * (1 / (averageCharacterCount * 2) )\\
        and \\
        wordYaxisOverlap > \\
        min(word1.height, word2.height) * requiredYaxisOverlap\\
    then \\
        combineWords
\end{equation}
The optimal parameters we found are $averageCharacterCount=8$ and $requiredYaxisOverlap=1/2$
Given that these conditions are fulfilled, we can combine both contours into one single contour, containing the found word.

@@

\subsection{Line selection}
As the ordening of the words % TODO, verklaar waarom die ordening weggat? 
we place the words in lines, and orden these lines. 
Algorithm \ref{alg:linereconstr} shows the pseudocode of our line selection process.
The algorithm reorders the words in lines and orders these lines as ordered in the original text.
